  
# This is me learning how to create a ggplot

library(tidyverse)

ggplot2::mpg
ggplot(data = mpg)+
  geom_point(mapping=aes(x=displ,y=hwy, color=class,shape=drv))
 
#This is the template for making graphs with ggplot  
```{r}
ggplot(data = <DATA>)+
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```

ggplot(data=mpg) 
mpg  
str(mpg$drv)
?mpg
ggplot(data = mpg)+
  geom_point(mapping = aes(x=class,y=drv))
  
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy),color = "blue")
  
  
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 3)  

  
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv~cyl)  
  
  
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)  
  
  
  
  
  
  
# This is some other advanced stuff from class that i will come back to
library(tidyverse)
  
  
```{r}
tibble(
  x=1:5,
  y=1,
  z= x^2+y
)
```






```{r}
tb<-tibble(
  ';)'="smile",
  ' '="space",
  '2000'="number"
)
tb
```

  str(parse_logical(c("TRUE", "FALSE", "NA")))
  


